---
format: gfm
title: ipapi-r
---

[![R-CMD-check](https://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml)

An R package to query IP addresses using the ipquery.io API.

## Installation

Install the package from GitHub using:

```r
remotes::install_github("josiahparry/ipapi-r")
```

## Usage

First, load the package. 

```{r}
library(ipapi)
```

```{r, include = FALSE}
library(pillar)
```

### Query a Specific IP Address

The `query_ips()` function retrieves information about IP addresses, including its ISP, location, and risk data.

```{r}
query_ips(c("8.8.8.8", "1.1.1.1"))
```

### Fetch Your Own Public IP Address

The `query_own_ip()` function retrieves the public IP address of the current machine.

```{r, eval = FALSE}
query_own_ip()
```
```{r, echo = FALSE}
res <- data.frame(
  ip = "203.0.113.45",
  asn = "AS0",
  org = "",
  isp = "",
  country = "",
  country_code = "",
  city = "",
  state = "",
  zipcode = "",
  latitude = 0.0142515998133369,
  longitude = -0.008837990871860742,
  timezone = "",
  localtime = "2025-01-02T15:55:33",
  is_mobile = FALSE,
  is_vpn = FALSE,
  is_tor = FALSE,
  is_proxy = FALSE,
  is_datacenter = FALSE,
  risk_score = 0L
)
structure(res, class = c("tbl", "data.frame"))
```