---
format: gfm
title: ipapi-r
---

[![R-CMD-check](https://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svghttps://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JosiahParry/ipapi-r/actions/workflows/R-CMD-check.yaml)

An R package to query IP addresses using the ipquery.io API.

## Installation

Install the package from GitHub using:

```r
remotes::install_github("josiahparry/ipapi-r")
```

## Usage

First, load the package. 

```{r}
library(ipapi)
```

```{r, include = FALSE}
library(pillar)
```

### Query a Specific IP Address

The `query_ips()` function retrieves information about IP addresses, including its ISP, location, and risk data.

```{r}
query_ips(c("8.8.8.8", "1.1.1.1"))
```

### Fetch Your Own Public IP Address

The `query_own_ip()` function retrieves the public IP address of the current machine.

```{r, eval = FALSE}
query_own_ip()
```
```{r, echo = FALSE}
"203.0.113.45"
```